---
title: "FARS Functions Package Vignette"
author: "Alfredo Alvarado"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
  
vignette: >
  %\VignetteIndexEntry{FARS TEST Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is the Vignette created for the package "Fars Functions"" as part of the coursera "Building an R Package" course.

The functions use data from the [US National Highway Traffic Safety Administration's Fatality Analysis Reporting System](https://www.nhtsa.gov/), which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.

## Functions that are part of the package

1. fars_map_state
1. fars_read
1. fars_read_years
1. fars_summarize_years
1. make_filename

## 1-fars_map_state
**Description:**
This function takes a year and state numbers and create a graph with the Highway Traffic
Fatality located by longitud and latitude.
The function will provide the warnings and messages included in the fars_read and make_file.

**Example on how it should be used:**
```{r, eval=FALSE}
setwd("~/Desktop/COURSERA/R Software Develpment specialization/Course3/1 test/data1/data")
library(Prueba1)
fars_map_state(c(20,33,48), c(2013,2014,2015))

```

## 2-fars_read
**Description:**
This function takes as "input" the name of the file and return a
dataframe using the readr::read_csv function.

**Example on how it should be used: **

```{r, eval=FALSE}
setwd("~/Desktop/COURSERA/R Software Develpment specialization/Course3/1 test/data1/data")
library(Prueba1)
fars_read("accident_2013d.csv.bz2")

```

## 3-fars_read_years
**Description:**
This function takes a vector of years as input, and them select the year and month information contained in
the files (like "accident_YYYYd.csv.bz2") saved in the working directory.
The files will be the ones where the name includes one of the years provided, after appliying
the "make_filename" function.

**Example on how it should be used: **

```{r, eval=FALSE}

setwd("~/Desktop/COURSERA/R Software Develpment specialization/Course3/1 test/data1/data")
library(Prueba1)
fars_read_years(c(2013,2014,2015))

```

## 4-fars_summarize_years

**Description:**
This function takes a vector of years, select and summarize the observations by year and month contained
in the files "accident_YYYYd.csv.bz2". The function will provide the warnings and messages included in the
fars_read and fars_read_years functions.

**Example on how it should be used:**
```{r, eval=FALSE}

setwd("~/Desktop/COURSERA/R Software Develpment specialization/Course3/1 test/data1/data")
library(Prueba1)
fars_summarize_years (c(2013,2014,2015))

```

## 5-make_filename

**Description:**
This function create a file name based on a given "year" that is part of the file name.
**Example on how it should be used:**
```{r, eval=FALSE}

setwd("~/Desktop/COURSERA/R Software Develpment specialization/Course3/1 test/data1/data")
library(Prueba1)
example1<-make_filename(2013)
example1

```


